### 2021-02-27 math/ia_2021/paper.tex
ia work

The data is cleaned of all "dubious" reports, reports before the year 1960 (see above), and
of all irrelevant fields such as "Injuries" or "Damage \$Mil". This preliminary data cleanup
is done through the use of the pandas Python library \cite{reback2020pandas}\cite{mckinney-proc-scipy-2010},

@@

Regression analysis is a commonly used tool in statistics, and regression models can
be found in numerous use cases. Regression models consist of estimating the
relationship between one (or more) independent variables and a dependent variable. A
simple example of regression can be seen in the linear relationship between an independent
variable $x_{i}$, and the dependent variable $y$. The following expression shows this relationship in what is
called linear regression, as it models a straight line.

$y = a + \beta x + e $,

where the term $a$ represents the y-intercept of the line and $\beta$ represents the
coefficient of $x_i$. The final term $e$ is what is known as the error or residual
term. It is an estimate of the amount by which the predictions differ from the real
value.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{modelshowcase.jpeg}
    \label{fig:boat1}
\end{figure}

@@

The model's accuracy is then calculated, with the test dataset. At first, it was considered 
to use the \verb|accuracy_score| method from the \verb|sklearn.metrics| class was used for 
this task. This function calculates what is called the $R^2$ value, which is a measure used to 
evaluate the fit a model on the dataset.

\section{Uses of this research}

>>>>

The data is cleaned of data points marked as "dubious" (there is an column for this parameter), 
reports before the year 1960 (see above), and of all irrelevant fields such as "Injuries" 
or "Damage \$Mil". This preliminary data cleanup
is done through the use of the pandas Python library \cite{reback2020pandas}\cite{mckinney-proc-scipy-2010}, 
which is commonly used for the handling of large datasets for its efficiency.

@@

Regression analysis is a commonly used tool in statistics, and regression models can
be found in numerous use cases. Regression models consist of estimating the
relationship between one (or more) independent variables and a dependent variable. A
simple example of regression can be seen in the linear relationship between an independent
variable $x_{i}$, and the dependent variable $y$. The following expression shows this relationship in what is
called linear regression, as it models a straight line that can be used for prediction of 
values:

$y =  \beta_0 a + \beta_1 x + e $,

where the term $\beta_0$ represents the y-intercept of the line and $\beta$ represents the
coefficient of $x$. The final term $e$ is what is known as the error or residual
term. It is an estimate of the amount by which the predictions differ from the real
value.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\textwidth]{modelshowcase.jpeg}
    \label{fig:boat1}
\end{figure}

@@

The model's fit is then calculated, with the test dataset. The \verb|accuracy_score| method 
from the \verb|sklearn.metrics| class was used for this task. This function calculates what 
is called the $R^2$ value, which explains the extent at which the variance (the amount by which numbers 
are spread from the average value) in the dependent variable can be explained by the independent 
variable(s). An $R^2$ value of 0.6 indicates that 60\% of the model's results match those of the 
dataset. This value is defined as:

$R^2 = 1 - \frac{SS_{res}}{SS_{total}}$,

where $SS_{res}$ is the sum of the error terms, or the residual sum of squares, in a dataset of $n$ 
values $y_1,\dots, y_i$, with their corresponding predicted values $p_1,\dots, p_i$ defined by

$SS_{res} = \sum_{i} (y_i - p_i)^2 = \sum_{i} e_i^2$, \footnote{$\sum_i i$ would mean that all values i 
are summed} where $e_i$ is the error term, equal to the difference of a data point $y_i$ 
and its corresponding predicted value $p_i$.

and $SS_{tot}$ is the total sum of squares, which is proportional to the variance in the data, 
defined as:

$SS_{tot} = \sum_{i} (y_i - \bar y)^2$, where $\bar y$ is the mean of the data $y_1,\dots, y_i$, 
or $\bar y = \frac{1}{n} \sum_{i=1}^n y_i$
